Kyoto VR MQP Paper First Draft

### 2019-09-24 paper.tex
continued introduction

Tourism and art are among the fields that could gain the most from AR
technology~\autocite{saenz2009, katz2018}.

@@

\subsection{Kinkaku-ji}
\label{sec:kinkaku-ji}

We were tasked with building an AR mobile app that enhances the experience of
visiting Kinkaku-ji, or the Golden Pavilion. As of September 2019, Kinkaku-ji
is the second-most visited site in Kyoto---second only to Kyoto Station
\autocite{japanguide2019}.

@@

The goal of Editour is to allow a non-technical user to design audio tours
through a web-app. At its core, Editour is a tool to draw arbitarily-shaped
geographic regions onto a map.

An audio file and multiple image files can be uploaded for each region the user
defines. The user can also provide a text transcript of the audio file as well.
After naming and uploading the tour with the ``Upload'' button, our backend
builds a zip containing a folder that can be placed directly into the Unity
project.

@@

\begin{minted}{json}
{
   "regions": [
      {
         "name": "Beautiful Place",
         "points": [ {"lat": 23.4, "lng": 56.7}, /* list omitted for brevity */ ],
         "audio": [ "beautiful-audio.mp3" ],
         "images": [ "mountain.jpg", "stream.jpg" ],
         "transcript": "To your left, you can see a beautiful place."
      },
      {
         "name": "Gorgeous Place",
         "points": [ {"lat": 12.3, "lng": 45.6}, /* list omitted for brevity */ ],
         "audio": [ "gorgeous-audio.mp3" ],
         "images": [ "hill.jpg", "valley.jpg", "gorge.jpg" ],
         "transcript", "To your right, you can see a gorgeous place."
      }
   ]
}
\end{minted}

Within each object in the region list, we can see that the region has five
properties: a name, a list of coordinates, a list of audio files, a list of
multiple image files, and a transcript of the audio file. (In the current
design of the app, it only makes sense to associate one audio file per region,
but the format makes it easy to accommodate for multiple audio files in the
future.) One disadvantage is that all media files have to have unique names.
This is because the zip that is created by the Editour backend contains all of
the media files in a flat file structure. The above JSON is used to associate
each media file with a region, meaning that the filename needs to act as a
primary key. The backend will respond with a message if this is the case,
prompting the user to have unique names for all files.

@@

The design of the Editour is agnostic about how the media will be used. For an
app like izi.TRAVEL, the images are displayed when the associated audio tour is
playing. The tour files produced by Editour could theoretically be used by a
tour guide app that does not incorporate AR.

>>>>

Tourism and art are among the fields that could gain the most from AR
technology~\autocite{saenz2009, katz2018}. AR technology can provide accessible
information to tourists and art viewers that they would not be able to get any
other way.

Kinkaku-ji, the ``golden pavilion'' of Kyoto, is the perfect example of
this~\autocite{bornoff2000}.

@@

@@

The goal of Editour is to allow a non-technical user to design audio tours
through a web-app. At its core, Editour is a tool to draw arbitarily-shaped
geographic regions onto a map. An audio file and multiple image files can be
uploaded for each region the user defines. After naming and uploading the tour
with the ``Upload'' button, our backend builds a zip containing a folder that can
be placed directly into the Unity project.

@@

\begin{minted}{json}
{
   "regions": [
      {
         "name": "Beautiful Place",
         "points": [ {"lat": 23.4, "lng": 56.7}, /* list omitted for brevity */ ],
         "audio": [ "beautiful-audio.mp3" ],
         "images": [ "mountain.jpg", "stream.jpg" ]
      },
      {
         "name": "Gorgeous Place",
         "points": [ {"lat": 12.3, "lng": 45.6}, /* list omitted for brevity */ ],
         "audio": [ "gorgeous-audio.mp3" ],
         "images": [ "hill.jpg", "valley.jpg", "gorge.jpg" ]
      }
   ]
}
\end{minted}

Within each object in the region list, we can see that the region has four
properties: a name, a list of coordinates, a list of audio files, and a list of
multiple image files. (In the current design of the app, it only makes sense to
associate one audio file per region, but the format makes it easy to
accommodate for multiple audio files in the future.) One disadvantage is that
all media files have to have unique names. This is because the zip that is
created by the Editour backend contains all of the media files in a flat file
structure. The above JSON is used to associate each media file with a region,
meaning that the filename needs to act as a primary key. The backend will
respond with a message if this is the case, prompting the user to have unique
names for all files.

@@

The design of the Editour is agnostic about how the media will be used.  For
an app like izi.TRAVEL, the images are displayed when the associated audio
tour is playing. For ARuku, images can be placed onto the ground plane by the
user, which is unique compared to other audio tour guide apps. The tour files
produced by Editour could theoretically be used by a tour guide app that does
not incorporate AR.
